WrapITK: Enhanced languages support\\ for the Insight Toolkit

### 2006-04-27 article/Article.tex
import vtk module before returning a vtk object to fix the segfault and deprecate itkvtk
darcs-hash:20060427201314-2fc9d-7788977ca5a53d1ddceea3ad0202e277f56927a1.gz

By default, those classes are not loaded in the \verb$itk$ module to avoid loading
all the \verb$vtk$ module while importing \verb$itk$. The command \verb$import itkvtk$
will load the module, and add the classes both in \verb$itkvtk$ and \verb$itk$ module.
The classes are then usable as the other itk classes.

@@

2> import itkvtk

3> reader = itk.ImageFileReader.IUC3.New()

4> converter = itk.ImageToVTKImageFilter.IUC3.New(reader)

5> converter.GetOutput()
5> <libvtkFilteringPython.vtkImageData vtkobject at 0xb7675b60>
\end{verbatim}

>>>>

With the python lazy loading, the classes are not loaded by default, and thus avoid
loading the entire vtk code in memory. The classes are directly available in the
\verb$itk$ module, and the underlaying code is loaded only when those classes are used.

@@

2> reader = itk.ImageFileReader.IUC3.New()

3> converter = itk.ImageToVTKImageFilter.IUC3.New(reader)

4> converter.GetOutput()
4> <libvtkFilteringPython.vtkImageData vtkobject at 0xb7675b60>
\end{verbatim}
